### 2021-10-13 content/80.formal-definition.tex
Escape # inside math mode

\begin{eqnarray*}
\mathcal{L}_{RDF}           & \equiv &      \big\{ Triple(s,p,o), IRI(i), BlankNode(b), Literal(s),
    \mathbb{IRI}, \mathbb{S}, \mathbb{R}    \big\} \\
\mathbb{D}_{RDF}            & \equiv &      \mathbb{S} \\
\forall i \ IRI(i)          & \Rightarrow & i \in \mathbb{IRI} \\
\forall s \forall p \forall o \
    Triple(s,p,o)           & \Rightarrow & \Big( IRI(s) \lor BlankNode(s) \Big) \land  \\
                            & &             IRI(p) \land  \\
                            & &             \Big(IRI(o) \lor BlankNode(o) \lor Literal(o) \Big) \\
Literal(v)                  & \models &     Value(v) \land Datatype(v,t) \land IRI(t) \\
\forall v \ Value(v)        & \Rightarrow & v \in \mathbb{S} \\
LanguageTag(v, l)           & \equiv &      Datatype\big(v, \\
    && \texttt{<http://www.w3.org/1999/02/22-rdf-syntax-ns#langString>}\big)
\end{eqnarray*}

@@

\begin{eqnarray*}
Property(p)         & \Rightarrow &     type(p, \texttt{<http://www.w3.org/2000/01/rdf-schema#Property>})   \\
Class(c)            & \Rightarrow &     type(c, \texttt{<http://www.w3.org/2000/01/rdf-schema#Class>})  \\
Dataset(d)          & \Rightarrow &     type(d, \texttt{<http://schema.org/Dataset>})   \\
File(f)             & \Rightarrow &     type(f, \texttt{<http://schema.org/MediaObject>})   \\
CreativeWork(e)     & \Rightarrow &     ContextualEntity(e) \land type(e, \texttt{<http://schema.org/CreativeWork>})  \\
hasPart(e, t)       & \Rightarrow &     Relation(e, \texttt{<http://schema.org/hasPart>}, t)    \\
name(e, n)          & \Rightarrow &     Attribute(e, \texttt{<http://schema.org/name>}, n)  \\
description(e, s)   & \Rightarrow &     Attribute(e, \texttt{<http://schema.org/description>}, s)   \\
datePublished(e, d) & \Rightarrow &     Attribute(e, \texttt{<http://schema.org/datePublished>}, d) \\
license(e, l)       & \Rightarrow &     Relation(e, \texttt{<http://schema.org/license>}, l) \land CreativeWork(l) \\
type(e, t)          & \Rightarrow &     Relation(e, \texttt{<http://www.w3.org/1999/02/22-rdf-syntax-ns#type>}, t) \\
                    & & \land Class(t)   \\
String(s)           & \equiv &          Value(s) \land  s \in \mathbb{S} \\
String(s)           & \Rightarrow &     Datatype(s, \texttt{<http://www.w3.org/2001/XMLSchema#string>}) \\
Decimal(d)          & \equiv &          Value(d) \land  d \in \mathbb{R} \\
Decimal(d)          & \Rightarrow &     Datatype(d, \texttt{<http://www.w3.org/2001/XMLSchema#decimal>}) \\
Relation(s,p,o)     & \Rightarrow &     Triple(s,p,o) \land IRI(s) \land IRI(o) \\
Attribute(s,p,o)    & \Rightarrow &     Triple(s,p,o) \land IRI(s) \land Literal(o) \\
\end{eqnarray*}

>>>>

\begin{eqnarray*}
\mathcal{L}_{RDF}           & \equiv &      \big\{ Triple(s,p,o), IRI(i), BlankNode(b), Literal(s),
    \mathbb{IRI}, \mathbb{S}, \mathbb{R}    \big\} \\
\mathbb{D}_{RDF}            & \equiv &      \mathbb{S} \\
\forall i \ IRI(i)          & \Rightarrow & i \in \mathbb{IRI} \\
\forall s \forall p \forall o \
    Triple(s,p,o)           & \Rightarrow & \Big( IRI(s) \lor BlankNode(s) \Big) \land  \\
                            & &             IRI(p) \land  \\
                            & &             \Big(IRI(o) \lor BlankNode(o) \lor Literal(o) \Big) \\
Literal(v)                  & \models &     Value(v) \land Datatype(v,t) \land IRI(t) \\
\forall v \ Value(v)        & \Rightarrow & v \in \mathbb{S} \\
LanguageTag(v, l)           & \equiv &      Datatype\big(v, \\
    && \texttt{<http://www.w3.org/1999/02/22-rdf-syntax-ns\#langString>}\big)
\end{eqnarray*}

@@

\begin{eqnarray*}
Property(p)         & \Rightarrow &     type(p, \texttt{<http://www.w3.org/2000/01/rdf-schema\#Property>})   \\
Class(c)            & \Rightarrow &     type(c, \texttt{<http://www.w3.org/2000/01/rdf-schema\#Class>})  \\
Dataset(d)          & \Rightarrow &     type(d, \texttt{<http://schema.org/Dataset>})   \\
File(f)             & \Rightarrow &     type(f, \texttt{<http://schema.org/MediaObject>})   \\
CreativeWork(e)     & \Rightarrow &     ContextualEntity(e) \land type(e, \texttt{<http://schema.org/CreativeWork>})  \\
hasPart(e, t)       & \Rightarrow &     Relation(e, \texttt{<http://schema.org/hasPart>}, t)    \\
name(e, n)          & \Rightarrow &     Attribute(e, \texttt{<http://schema.org/name>}, n)  \\
description(e, s)   & \Rightarrow &     Attribute(e, \texttt{<http://schema.org/description>}, s)   \\
datePublished(e, d) & \Rightarrow &     Attribute(e, \texttt{<http://schema.org/datePublished>}, d) \\
license(e, l)       & \Rightarrow &     Relation(e, \texttt{<http://schema.org/license>}, l) \land CreativeWork(l) \\
type(e, t)          & \Rightarrow &     Relation(e, \texttt{<http://www.w3.org/1999/02/22-rdf-syntax-ns\#type>}, t) \\
                    & & \land Class(t)   \\
String(s)           & \equiv &          Value(s) \land  s \in \mathbb{S} \\
String(s)           & \Rightarrow &     Datatype(s, \texttt{<http://www.w3.org/2001/XMLSchema\#string>}) \\
Decimal(d)          & \equiv &          Value(d) \land  d \in \mathbb{R} \\
Decimal(d)          & \Rightarrow &     Datatype(d, \texttt{<http://www.w3.org/2001/XMLSchema\#decimal>}) \\
Relation(s,p,o)     & \Rightarrow &     Triple(s,p,o) \land IRI(s) \land IRI(o) \\
Attribute(s,p,o)    & \Rightarrow &     Triple(s,p,o) \land IRI(s) \land Literal(o) \\
\end{eqnarray*}
